Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2024-08-08 paper/main.tex
Updates

In this section, we develop a novel partial measure of association for mixed
data by extending partial correlations to mixed data. As partial correlations
require two things: 1) A residualization method, and 2) measure of associations
between the residuals. We generalize this to mixed data by combining a mixed
data residualization method \citep{Ankan2023} with a multivariate measure of
association based on Pillai's Trace. Given $ n $ samples $ D = (x, y, \bm{z}) $
of variables $ X $, $ Y $, and $ \bm{Z} $, we are interested in computing an
estimate of the conditional association $ \rho(X, Y; \bm{Z}) $ between $ X $
and $ Y $ conditioned on $ \bm{Z} $. As the residualization approach requires
atleast one conditional variable to be present, if $ \bm{Z} = \emptyset $, we
use a constant value for $ Z $. Similar to partial correlation, we first
compute the residuals for $ X $ and $ Y $ using $ \bm{Z} $ as the predictor
variables. We use the mixed data residualization approach from
\citet{Ankan2023}. Depending on the type of dependent variable, the residuals
are defined as follows:

>>>>

In this section, we develop a novel measure of partial association for mixed
data by extending partial correlations \citep{Whittaker2009} \todo{Verify this
citation} to mixed data.
As partial correlations require two things: 1) A
residualization method, and 2) measure of associations between the residuals.
We generalize this to mixed data by combining a mixed data residualization
method \citep{Ankan2023} with a multivariate measure of association based on
Pillai's Trace. Given $ n $ samples $ D = (x, y, \bm{z}) $ of variables $ X $,
$ Y $, and $ \bm{Z} $, we are interested in computing an estimate of the
conditional association $ \rho(X, Y; \bm{Z}) $ between $ X $ and $ Y $
conditioned on $ \bm{Z} $. As the residualization approach requires atleast one
conditional variable to be present, if $ \bm{Z} = \emptyset $, we use a
constant value for $ Z $. Similar to partial correlation, we first compute the
residuals for $ X $ and $ Y $ using $ \bm{Z} $ as the predictor variables. We
use the mixed data residualization approach from \citet{Ankan2023}. Depending
on the type of dependent variable, the residuals are defined as follows:
